Parental migration and adolescent's educational performance

### 2022-05-23 data/Gu-thesis-script.Rmd
change template

---
title: "Parental migration, cognitive development and educational performance"
output: html_notebook
---

@@

```{r}
d <- d %>% mutate(
  age = 2014 - a02a, #children's age at baseline
  local.resi = age - a07 #years of residence at the current county05
)
```

@@

Sample
```{r}
d_cl <- d_cl %>% 
  filter(w2a0801==1) %>% #parents who are married (and alive)
  filter(be1201==1 & be1202==1) %>% #both parents stay with children at baseline
  filter(local.resi>=7)
```

@@

## Treatment groups
At least one parent migrated (Control group as no parent migrated)
```{r}
d_cl <- d_cl %>% mutate(
  treat_leave = if_else((w2ba0201==0 | w2ba0202==0), 1, 0), #Any parent became absent from household between baseline and endline survey
  treat_fa_only = NA,
  treat_mo_only = NA,
  treat_both = NA
  )
```

Only mother migrated
```{r}
d_cl$treat_mo_only[d_cl$treat_leave == 0] <- 0
d_cl$treat_mo_only[d_cl$w2ba0201==1 & d_cl$w2ba0202==0] <- 1 
```

Mother migrated
```{r}
d_cl$treat_mo[d_cl$treat_leave == 0] <- 0
d_cl$treat_mo[d_cl$w2ba0202==0] <- 1
```

Only father migrated
```{r}
d_cl$treat_fa_only[d_cl$treat_leave == 0] <- 0
d_cl$treat_fa_only[d_cl$w2ba0201==0 & d_cl$w2ba0202==1] <- 1 
```

Father migrated
```{r}
d_cl$treat_fa[d_cl$treat_leave == 0] <- 0
d_cl$treat_fa[d_cl$w2ba0201==0] <- 1
```

Both parents migrated
```{r}
d_cl$treat_both[d_cl$treat_leave == 0] <- 0
d_cl$treat_both[d_cl$w2ba0201==0 & d_cl$w2ba0202==0] <- 1
```

@@

### Wave 2 outcomes of treatment group vs control group
```{r}
d_cl %>%
  group_by(treat_leave) %>% 
  summarise(n_cases = n(),
            mean_cog = mean(w2cog3pl, na.rm=T),
            mean_ttl = mean(w2ttl_std, na.rm=T),
            mean_chn = mean(w2chn_std, na.rm=T),
            mean_mat = mean(w2mat_std, na.rm=T),
            mean_eng = mean(w2eng_std, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(treat_mo_only) %>% 
  summarise(n_cases = n(),
            mean_cog = mean(w2cog3pl, na.rm=T),
            mean_ttl = mean(w2ttl_std, na.rm=T),
            mean_chn = mean(w2chn_std, na.rm=T),
            mean_mat = mean(w2mat_std, na.rm=T),
            mean_eng = mean(w2eng_std, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(treat_mo) %>% 
  summarise(n_cases = n(),
            mean_cog = mean(w2cog3pl, na.rm=T),
            mean_ttl = mean(w2ttl_std, na.rm=T),
            mean_chn = mean(w2chn_std, na.rm=T),
            mean_mat = mean(w2mat_std, na.rm=T),
            mean_eng = mean(w2eng_std, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(treat_fa_only) %>% 
  summarise(n_cases = n(),
            mean_cog = mean(w2cog3pl, na.rm=T),
            mean_ttl = mean(w2ttl_std, na.rm=T),
            mean_chn = mean(w2chn_std, na.rm=T),
            mean_mat = mean(w2mat_std, na.rm=T),
            mean_eng = mean(w2eng_std, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(treat_fa) %>% 
  summarise(n_cases = n(),
            mean_cog = mean(w2cog3pl, na.rm=T),
            mean_ttl = mean(w2ttl_std, na.rm=T),
            mean_chn = mean(w2chn_std, na.rm=T),
            mean_mat = mean(w2mat_std, na.rm=T),
            mean_eng = mean(w2eng_std, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(treat_both) %>% 
  summarise(n_cases = n(),
            mean_cog = mean(w2cog3pl, na.rm=T),
            mean_ttl = mean(w2ttl_std, na.rm=T),
            mean_chn = mean(w2chn_std, na.rm=T),
            mean_mat = mean(w2mat_std, na.rm=T),
            mean_eng = mean(w2eng_std, na.rm=T)
            ) %>%
  drop_na()
```

### Change in outcomes of treatment group vs control group
```{r}
d_cl %>%
  group_by(treat_leave) %>% 
  summarise(n_cases = n(),
            mean_change_cog = mean(cog, na.rm=T),
            mean_change_ttl = mean(ttl_std, na.rm=T),
            mean_change_chn = mean(chn_std, na.rm=T),
            mean_change_mat = mean(mat_std, na.rm=T),
            mean_change_eng = mean(eng_std, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(treat_mo_only) %>% 
  summarise(n_cases = n(),
            mean_cog = mean(w2cog3pl, na.rm=T),
            mean_ttl = mean(w2ttl_std, na.rm=T),
            mean_chn = mean(w2chn_std, na.rm=T),
            mean_mat = mean(w2mat_std, na.rm=T),
            mean_eng = mean(w2eng_std, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(treat_mo) %>% 
  summarise(n_cases = n(),
            mean_change_cog = mean(cog, na.rm=T),
            mean_change_ttl = mean(ttl_std, na.rm=T),
            mean_change_chn = mean(chn_std, na.rm=T),
            mean_change_mat = mean(mat_std, na.rm=T),
            mean_change_eng = mean(eng_std, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(treat_fa_only) %>% 
  summarise(n_cases = n(),
            mean_change_cog = mean(cog, na.rm=T),
            mean_change_ttl = mean(ttl_std, na.rm=T),
            mean_change_chn = mean(chn_std, na.rm=T),
            mean_change_mat = mean(mat_std, na.rm=T),
            mean_change_eng = mean(eng_std, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(treat_fa) %>% 
  summarise(n_cases = n(),
            mean_change_cog = mean(cog, na.rm=T),
            mean_change_ttl = mean(ttl_std, na.rm=T),
            mean_change_chn = mean(chn_std, na.rm=T),
            mean_change_mat = mean(mat_std, na.rm=T),
            mean_change_eng = mean(eng_std, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(treat_both) %>% 
  summarise(n_cases = n(),
            mean_change_cog = mean(cog, na.rm=T),
            mean_change_ttl = mean(ttl_std, na.rm=T),
            mean_change_chn = mean(chn_std, na.rm=T),
            mean_change_mat = mean(mat_std, na.rm=T),
            mean_change_eng = mean(eng_std, na.rm=T)
            ) %>%
  drop_na()
```

## DID basic
Regressing on cognitive test score (standardized)
```{r}
did_cog <- feols(cog ~ treat_leave | schids + ctyids, data = d_cl) 
did_cog_m_only <- feols(cog ~ treat_mo_only | schids + ctyids, data = d_cl) 
did_cog_m <- feols(cog ~ treat_mo | schids + ctyids, data = d_cl) 
did_cog_f_only <- feols(cog ~ treat_fa_only | schids + ctyids, data = d_cl) 
did_cog_f <- feols(cog ~ treat_fa | schids + ctyids, data = d_cl) 
did_cog_both <- feols(cog ~ treat_both | schids + ctyids, data = d_cl)
```
Results
```{r}
models_cog <- list(
did_cog,
did_cog_m_only,
did_cog_m,
did_cog_f,
did_cog_f_only,
did_cog_both) 
models_cog %>% msummary(stars = c('*' = .1, '**' = .05, '***' = .01))
```
Regressing on total exam score
```{r}
did_ttl <- feols(ttl_std ~ treat_leave | schids + ctyids, data = d_cl) 
did_ttl_m_only <- feols(ttl_std ~ treat_mo_only | schids + ctyids, data = d_cl) 
did_ttl_m <- feols(ttl_std ~ treat_mo | schids + ctyids, data = d_cl) 
did_ttl_f <- feols(ttl_std ~ treat_fa | schids + ctyids, data = d_cl) 
did_ttl_f_only <- feols(ttl_std ~ treat_fa_only | schids + ctyids, data = d_cl) 
did_ttl_both <- feols(ttl_std ~ treat_both | schids + ctyids, data = d_cl)
```
Results
```{r}
models_ttl <- list(
did_ttl,
did_ttl_m_only,
did_ttl_m,
did_ttl_f,
did_ttl_f_only,
did_ttl_both) 
models_ttl %>% msummary(stars = c('*' = .1, '**' = .05, '***' = .01))
```

Regressing on Chinese exam score
```{r}
did_chn <- feols(chn_std ~ treat_leave | schids + ctyids, data = d_cl) 
did_chn_m_only <- feols(chn_std ~ treat_mo_only | schids + ctyids, data = d_cl) 
did_chn_m <- feols(chn_std ~ treat_mo | schids + ctyids, data = d_cl) 
did_chn_f_only <- feols(chn_std ~ treat_fa_only | schids + ctyids, data = d_cl) 
did_chn_f <- feols(chn_std ~ treat_fa | schids + ctyids, data = d_cl) 
did_chn_both <- feols(chn_std ~ treat_both | schids + ctyids, data = d_cl)
```
Results
```{r}
models_chn <- list(
did_chn,
did_chn_m_only,
did_chn_m,
did_chn_f,
did_chn_f_only,
did_chn_both) 
models_chn %>% msummary(stars = c('*' = .1, '**' = .05, '***' = .01))
```

Regressing on Math score
```{r}
did_mat <- feols(mat_std ~ treat_leave | schids + ctyids, data = d_cl) 
did_mat_m_only <- feols(mat_std ~ treat_mo_only | schids + ctyids, data = d_cl) 
did_mat_m <- feols(mat_std ~ treat_mo | schids + ctyids, data = d_cl) 
did_mat_f_only <- feols(mat_std ~ treat_fa_only | schids + ctyids, data = d_cl) 
did_mat_f <- feols(mat_std ~ treat_fa | schids + ctyids, data = d_cl) 
did_mat_both <- feols(mat_std ~ treat_both | schids + ctyids, data = d_cl)
```
Results
```{r}
models_mat <- list(
did_mat,
did_mat_m_only,
did_mat_m,
did_mat_f,
did_mat_f_only,
did_mat_both) 
models_mat %>% msummary(stars = c('*' = .1, '**' = .05, '***' = .01))
```

Regressing on English score
```{r}
did_eng <- feols(eng_std ~ treat_leave | schids + ctyids, data = d_cl) 
did_eng_m <- feols(eng_std ~ treat_mo | schids + ctyids, data = d_cl)
did_eng_m_only <- feols(eng_std ~ treat_mo_only | schids + ctyids, data = d_cl) 
did_eng_f <- feols(eng_std ~ treat_fa | schids + ctyids, data = d_cl) 
did_eng_f_only <- feols(eng_std ~ treat_fa_only | schids + ctyids, data = d_cl) 
did_eng_both <- feols(eng_std ~ treat_both | schids + ctyids, data = d_cl)
```
Results
```{r}
models_eng <- list(
did_eng,
did_eng_m_only,
did_eng_m,
did_eng_f,
did_eng_f_only,
did_eng_both) 
models_eng %>% msummary(stars = c('*' = .1, '**' = .05, '***' = .01))
```

## DID unrestricted
Regressing on cognitive test score (standardized)
```{r}
did_unres_cog <- feols(cog ~ treat_leave + cog3pl | schids + ctyids, data = d_cl) 
did_unres_cog_m_only <- feols(cog ~ treat_mo_only + cog3pl | schids + ctyids, data = d_cl) 
did_unres_cog_m <- feols(cog ~ treat_mo + cog3pl | schids + ctyids, data = d_cl) 
did_unres_cog_f_only <- feols(cog ~ treat_fa_only + cog3pl | schids + ctyids, data = d_cl) 
did_unres_cog_f <- feols(cog ~ treat_fa + cog3pl | schids + ctyids, data = d_cl) 
did_unres_cog_both <- feols(cog ~ treat_both + cog3pl | schids + ctyids, data = d_cl)
```
Results
```{r}
models_unres_cog <- list(
did_unres_cog,
did_unres_cog_m_only,
did_unres_cog_m,
did_unres_cog_f,
did_unres_cog_f_only,
did_unres_cog_both) 
models_unres_cog %>% msummary(stars = c('*' = .1, '**' = .05, '***' = .01))
```
Regressing on total exam score
```{r}
did_unres_ttl <- feols(ttl_std ~ treat_leave + w1ttl_std | schids + ctyids, data = d_cl) 
did_unres_ttl_m_only <- feols(ttl_std ~ treat_mo_only + w1ttl_std | schids + ctyids, data = d_cl) 
did_unres_ttl_m <- feols(ttl_std ~ treat_mo + w1ttl_std | schids + ctyids, data = d_cl) 
did_unres_ttl_f <- feols(ttl_std ~ treat_fa + w1ttl_std | schids + ctyids, data = d_cl) 
did_unres_ttl_f_only <- feols(ttl_std ~ treat_fa_only + w1ttl_std | schids + ctyids, data = d_cl) 
did_unres_ttl_both <- feols(ttl_std ~ treat_both + w1ttl_std | schids + ctyids, data = d_cl)
```
Results
```{r}
models_unres_ttl <- list(
did_unres_ttl,
did_unres_ttl_m_only,
did_unres_ttl_m,
did_unres_ttl_f,
did_unres_ttl_f_only,
did_unres_ttl_both) 
models_unres_ttl %>% msummary(stars = c('*' = .1, '**' = .05, '***' = .01))
```

Regressing on Chinese exam score
```{r}
did_unres_chn <- feols(chn_std ~ treat_leave + w1chn_std | schids + ctyids, data = d_cl) 
did_unres_chn_m_only <- feols(chn_std ~ treat_mo_only + w1chn_std | schids + ctyids, data = d_cl) 
did_unres_chn_m <- feols(chn_std ~ treat_mo + w1chn_std | schids + ctyids, data = d_cl) 
did_unres_chn_f_only <- feols(chn_std ~ treat_fa_only + w1chn_std | schids + ctyids, data = d_cl) 
did_unres_chn_f <- feols(chn_std ~ treat_fa + w1chn_std | schids + ctyids, data = d_cl) 
did_unres_chn_both <- feols(chn_std ~ treat_both + w1chn_std | schids + ctyids, data = d_cl)
```
Results
```{r}
models_unres_chn <- list(
did_unres_chn,
did_unres_chn_m_only,
did_unres_chn_m,
did_unres_chn_f,
did_unres_chn_f_only,
did_unres_chn_both) 
models_unres_chn %>% msummary(stars = c('*' = .1, '**' = .05, '***' = .01))
```

Regressing on Math score
```{r}
did_unres_mat <- feols(mat_std ~ treat_leave + w1mat_std | schids + ctyids, data = d_cl) 
did_unres_mat_m_only <- feols(mat_std ~ treat_mo_only + w1mat_std | schids + ctyids, data = d_cl) 
did_unres_mat_m <- feols(mat_std ~ treat_mo + w1mat_std | schids + ctyids, data = d_cl) 
did_unres_mat_f_only <- feols(mat_std ~ treat_fa_only + w1mat_std | schids + ctyids, data = d_cl) 
did_unres_mat_f <- feols(mat_std ~ treat_fa + w1mat_std | schids + ctyids, data = d_cl) 
did_unres_mat_both <- feols(mat_std ~ treat_both + w1mat_std | schids + ctyids, data = d_cl)
```
Results
```{r}
models_unres_mat <- list(
did_unres_mat,
did_unres_mat_m_only,
did_unres_mat_m,
did_unres_mat_f,
did_unres_mat_f_only,
did_unres_mat_both) 
models_unres_mat %>% msummary(stars = c('*' = .1, '**' = .05, '***' = .01))
```

Regressing on English score
```{r}
did_unres_eng <- feols(eng_std ~ treat_leave + w1eng_std | schids + ctyids, data = d_cl) 
did_unres_eng_m <- feols(eng_std ~ treat_mo + w1eng_std | schids + ctyids, data = d_cl)
did_unres_eng_m_only <- feols(eng_std ~ treat_mo_only + w1eng_std | schids + ctyids, data = d_cl) 
did_unres_eng_f <- feols(eng_std ~ treat_fa + w1eng_std | schids + ctyids, data = d_cl) 
did_unres_eng_f_only <- feols(eng_std ~ treat_fa_only + w1eng_std | schids + ctyids, data = d_cl) 
did_unres_eng_both <- feols(eng_std ~ treat_both + w1eng_std | schids + ctyids, data = d_cl)
```
Results
```{r}
models_unres_eng <- list(
did_unres_eng,
did_unres_eng_m_only,
did_unres_eng_m,
did_unres_eng_f,
did_unres_eng_f_only,
did_unres_eng_both) 
models_unres_eng %>% msummary(stars = c('*' = .1, '**' = .05, '***' = .01))
```

>>>>

---
title: "Parental migration and adolescent's educational performance"
output: html_notebook
---

@@

```{r}
d <- d %>% mutate(
  age = 2013 - a02a, #student's age at baseline
  local.resi = age - a07 #years of residence at the current county
)
```

@@

Sample
```{r}
d_cl <- d %>% 
  filter(w2a0801==1) %>% #parents who are married (and alive)
  filter(be1201==1 & be1202==1) %>% #both parents live with children at baseline
  filter(local.resi>=6) #having stayed in the current county for at least six years (duration of primary school) before baseline
```

@@

## Treatment groups
At least one parent migrated (Control group as no parent migrated)
```{r}
d_cl <- d_cl %>% mutate(
  migr = if_else((w2ba0201==0 | w2ba0202==0), 1, 0), #Any parent became absent from household between baseline and endline survey
  migr_fa_only = NA,
  migr_fa = NA,
  migr_mo_only = NA,
  migr_mo = NA,
  migr_both = NA
  )
```

Only mother migrated
```{r}
d_cl$migr_mo_only[d_cl$migr == 0] <- 0
d_cl$migr_mo_only[d_cl$w2ba0201==1 & d_cl$w2ba0202==0] <- 1 
```

Mother migrated
```{r}
d_cl$migr_mo[d_cl$migr == 0] <- 0
d_cl$migr_mo[d_cl$w2ba0202==0] <- 1
```

Only father migrated
```{r}
d_cl$migr_fa_only[d_cl$migr == 0] <- 0
d_cl$migr_fa_only[d_cl$w2ba0201==0 & d_cl$w2ba0202==1] <- 1 
```

Father migrated
```{r}
d_cl$migr_fa[d_cl$migr == 0] <- 0
d_cl$migr_fa[d_cl$w2ba0201==0] <- 1
```

Both parents migrated
```{r}
d_cl$migr_both[d_cl$migr == 0] <- 0
d_cl$migr_both[d_cl$w2ba0201==0 & d_cl$w2ba0202==0] <- 1
```

@@

### Wave 2 outcomes of treatment group vs control group
```{r}
d_cl %>%
  group_by(migr) %>% 
  summarise(n_cases = n(),
            mean_cog = mean(w2cog3pl, na.rm=T),
            mean_ttl = mean(w2ttl_std, na.rm=T),
            mean_chn = mean(w2chn_std, na.rm=T),
            mean_mat = mean(w2mat_std, na.rm=T),
            mean_eng = mean(w2eng_std, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_mo_only) %>% 
  summarise(n_cases = n(),
            mean_cog = mean(w2cog3pl, na.rm=T),
            mean_ttl = mean(w2ttl_std, na.rm=T),
            mean_chn = mean(w2chn_std, na.rm=T),
            mean_mat = mean(w2mat_std, na.rm=T),
            mean_eng = mean(w2eng_std, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_mo) %>% 
  summarise(n_cases = n(),
            mean_cog = mean(w2cog3pl, na.rm=T),
            mean_ttl = mean(w2ttl_std, na.rm=T),
            mean_chn = mean(w2chn_std, na.rm=T),
            mean_mat = mean(w2mat_std, na.rm=T),
            mean_eng = mean(w2eng_std, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_fa_only) %>% 
  summarise(n_cases = n(),
            mean_cog = mean(w2cog3pl, na.rm=T),
            mean_ttl = mean(w2ttl_std, na.rm=T),
            mean_chn = mean(w2chn_std, na.rm=T),
            mean_mat = mean(w2mat_std, na.rm=T),
            mean_eng = mean(w2eng_std, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_fa) %>% 
  summarise(n_cases = n(),
            mean_cog = mean(w2cog3pl, na.rm=T),
            mean_ttl = mean(w2ttl_std, na.rm=T),
            mean_chn = mean(w2chn_std, na.rm=T),
            mean_mat = mean(w2mat_std, na.rm=T),
            mean_eng = mean(w2eng_std, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_both) %>% 
  summarise(n_cases = n(),
            mean_cog = mean(w2cog3pl, na.rm=T),
            mean_ttl = mean(w2ttl_std, na.rm=T),
            mean_chn = mean(w2chn_std, na.rm=T),
            mean_mat = mean(w2mat_std, na.rm=T),
            mean_eng = mean(w2eng_std, na.rm=T)
            ) %>%
  drop_na()
```

### Change in outcomes of treatment group vs control group
```{r}
d_cl %>%
  group_by(migr) %>% 
  summarise(n_cases = n(),
            mean_change_cog = mean(cog, na.rm=T),
            mean_change_ttl = mean(ttl_std, na.rm=T),
            mean_change_chn = mean(chn_std, na.rm=T),
            mean_change_mat = mean(mat_std, na.rm=T),
            mean_change_eng = mean(eng_std, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_mo_only) %>% 
  summarise(n_cases = n(),
            mean_cog = mean(w2cog3pl, na.rm=T),
            mean_ttl = mean(w2ttl_std, na.rm=T),
            mean_chn = mean(w2chn_std, na.rm=T),
            mean_mat = mean(w2mat_std, na.rm=T),
            mean_eng = mean(w2eng_std, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_mo) %>% 
  summarise(n_cases = n(),
            mean_change_cog = mean(cog, na.rm=T),
            mean_change_ttl = mean(ttl_std, na.rm=T),
            mean_change_chn = mean(chn_std, na.rm=T),
            mean_change_mat = mean(mat_std, na.rm=T),
            mean_change_eng = mean(eng_std, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_fa_only) %>% 
  summarise(n_cases = n(),
            mean_change_cog = mean(cog, na.rm=T),
            mean_change_ttl = mean(ttl_std, na.rm=T),
            mean_change_chn = mean(chn_std, na.rm=T),
            mean_change_mat = mean(mat_std, na.rm=T),
            mean_change_eng = mean(eng_std, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_fa) %>% 
  summarise(n_cases = n(),
            mean_change_cog = mean(cog, na.rm=T),
            mean_change_ttl = mean(ttl_std, na.rm=T),
            mean_change_chn = mean(chn_std, na.rm=T),
            mean_change_mat = mean(mat_std, na.rm=T),
            mean_change_eng = mean(eng_std, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_both) %>% 
  summarise(n_cases = n(),
            mean_change_cog = mean(cog, na.rm=T),
            mean_change_ttl = mean(ttl_std, na.rm=T),
            mean_change_chn = mean(chn_std, na.rm=T),
            mean_change_mat = mean(mat_std, na.rm=T),
            mean_change_eng = mean(eng_std, na.rm=T)
            ) %>%
  drop_na()
```

## DID basic
$$\Delta score_{i,s} = \alpha + \beta \cdot migr_{i,s} + \gamma \cdot FE_{s} + \varepsilon_{i,s} $$
For student i in school s, $$\Delta score_{i,s}$$ is the change in standardized test score between baseline survey and endline survey, $$migr_{i,s}$$ is the treatment dummy variable, and $$FE_{s}$$ is the school-level fixed effect.

Regressing on cognitive test score (standardized)
```{r}
did_cog <- feols(cog ~ migr | schids, data = d_cl) 
did_cog_m_only <- feols(cog ~ migr_mo_only | schids, data = d_cl) 
did_cog_m <- feols(cog ~ migr_mo | schids, data = d_cl) 
did_cog_f_only <- feols(cog ~ migr_fa_only | schids, data = d_cl) 
did_cog_f <- feols(cog ~ migr_fa | schids, data = d_cl) 
did_cog_both <- feols(cog ~ migr_both | schids, data = d_cl)
```

Results
```{r}
models_cog <- list(
did_cog,
did_cog_m_only,
did_cog_m,
did_cog_f,
did_cog_f_only,
did_cog_both) 
models_cog %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
```

Regressing on total exam score
```{r}
did_ttl <- feols(ttl_std ~ migr | schids, data = d_cl) 
did_ttl_m_only <- feols(ttl_std ~ migr_mo_only | schids, data = d_cl) 
did_ttl_m <- feols(ttl_std ~ migr_mo | schids, data = d_cl) 
did_ttl_f <- feols(ttl_std ~ migr_fa | schids, data = d_cl) 
did_ttl_f_only <- feols(ttl_std ~ migr_fa_only | schids, data = d_cl) 
did_ttl_both <- feols(ttl_std ~ migr_both | schids, data = d_cl)
```

Results
```{r}
models_ttl <- list(
did_ttl,
did_ttl_m_only,
did_ttl_m,
did_ttl_f,
did_ttl_f_only,
did_ttl_both) 
models_ttl %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
```

Regressing on Chinese exam score
```{r}
did_chn <- feols(chn_std ~ migr | schids, data = d_cl) 
did_chn_m_only <- feols(chn_std ~ migr_mo_only | schids, data = d_cl) 
did_chn_m <- feols(chn_std ~ migr_mo | schids, data = d_cl) 
did_chn_f_only <- feols(chn_std ~ migr_fa_only | schids, data = d_cl) 
did_chn_f <- feols(chn_std ~ migr_fa | schids, data = d_cl) 
did_chn_both <- feols(chn_std ~ migr_both | schids, data = d_cl)
```

Results
```{r}
models_chn <- list(
did_chn,
did_chn_m_only,
did_chn_m,
did_chn_f,
did_chn_f_only,
did_chn_both) 
models_chn %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
```

Regressing on Math score
```{r}
did_mat <- feols(mat_std ~ migr | schids, data = d_cl) 
did_mat_m_only <- feols(mat_std ~ migr_mo_only | schids, data = d_cl) 
did_mat_m <- feols(mat_std ~ migr_mo | schids, data = d_cl) 
did_mat_f_only <- feols(mat_std ~ migr_fa_only | schids, data = d_cl) 
did_mat_f <- feols(mat_std ~ migr_fa | schids, data = d_cl) 
did_mat_both <- feols(mat_std ~ migr_both | schids, data = d_cl)
```

Results
```{r}
models_mat <- list(
did_mat,
did_mat_m_only,
did_mat_m,
did_mat_f,
did_mat_f_only,
did_mat_both) 
models_mat %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
```

Regressing on English score
```{r}
did_eng <- feols(eng_std ~ migr | schids, data = d_cl) 
did_eng_m <- feols(eng_std ~ migr_mo | schids, data = d_cl)
did_eng_m_only <- feols(eng_std ~ migr_mo_only | schids, data = d_cl) 
did_eng_f <- feols(eng_std ~ migr_fa | schids, data = d_cl) 
did_eng_f_only <- feols(eng_std ~ migr_fa_only | schids, data = d_cl) 
did_eng_both <- feols(eng_std ~ migr_both | schids, data = d_cl)
```

Results
```{r}
models_eng <- list(
did_eng,
did_eng_m_only,
did_eng_m,
did_eng_f,
did_eng_f_only,
did_eng_both) 
models_eng %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
```

## DID unrestricted
$$\Delta score_{i,s} = \alpha + \beta \cdot migr_{i,s} + \lambda \cdot score_{i,s;base} + \gamma \cdot FE_{s} + \varepsilon_{i,s} $$
where baseline score is a variable on right hand side

Regressing on cognitive test score (standardized)
```{r}
did_unres_cog <- feols(cog ~ migr + cog3pl | schids, data = d_cl) 
did_unres_cog_m_only <- feols(cog ~ migr_mo_only + cog3pl | schids, data = d_cl) 
did_unres_cog_m <- feols(cog ~ migr_mo + cog3pl | schids, data = d_cl) 
did_unres_cog_f_only <- feols(cog ~ migr_fa_only + cog3pl | schids, data = d_cl) 
did_unres_cog_f <- feols(cog ~ migr_fa + cog3pl | schids, data = d_cl) 
did_unres_cog_both <- feols(cog ~ migr_both + cog3pl | schids, data = d_cl)
```

Results
```{r}
models_unres_cog <- list(
did_unres_cog,
did_unres_cog_m_only,
did_unres_cog_m,
did_unres_cog_f,
did_unres_cog_f_only,
did_unres_cog_both) 
models_unres_cog %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
```

Regressing on total exam score
```{r}
did_unres_ttl <- feols(ttl_std ~ migr + w1ttl_std | schids, data = d_cl) 
did_unres_ttl_m_only <- feols(ttl_std ~ migr_mo_only + w1ttl_std | schids, data = d_cl) 
did_unres_ttl_m <- feols(ttl_std ~ migr_mo + w1ttl_std | schids, data = d_cl) 
did_unres_ttl_f <- feols(ttl_std ~ migr_fa + w1ttl_std | schids, data = d_cl) 
did_unres_ttl_f_only <- feols(ttl_std ~ migr_fa_only + w1ttl_std | schids, data = d_cl) 
did_unres_ttl_both <- feols(ttl_std ~ migr_both + w1ttl_std | schids, data = d_cl)
```

Results
```{r}
models_unres_ttl <- list(
did_unres_ttl,
did_unres_ttl_m_only,
did_unres_ttl_m,
did_unres_ttl_f,
did_unres_ttl_f_only,
did_unres_ttl_both) 
models_unres_ttl %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
```

Regressing on Chinese exam score
```{r}
did_unres_chn <- feols(chn_std ~ migr + w1chn_std | schids, data = d_cl) 
did_unres_chn_m_only <- feols(chn_std ~ migr_mo_only + w1chn_std | schids, data = d_cl) 
did_unres_chn_m <- feols(chn_std ~ migr_mo + w1chn_std | schids, data = d_cl) 
did_unres_chn_f_only <- feols(chn_std ~ migr_fa_only + w1chn_std | schids, data = d_cl) 
did_unres_chn_f <- feols(chn_std ~ migr_fa + w1chn_std | schids, data = d_cl) 
did_unres_chn_both <- feols(chn_std ~ migr_both + w1chn_std | schids, data = d_cl)
```

Results
```{r}
models_unres_chn <- list(
did_unres_chn,
did_unres_chn_m_only,
did_unres_chn_m,
did_unres_chn_f,
did_unres_chn_f_only,
did_unres_chn_both) 
models_unres_chn %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
```

Regressing on Math score
```{r}
did_unres_mat <- feols(mat_std ~ migr + w1mat_std | schids, data = d_cl) 
did_unres_mat_m_only <- feols(mat_std ~ migr_mo_only + w1mat_std | schids, data = d_cl) 
did_unres_mat_m <- feols(mat_std ~ migr_mo + w1mat_std | schids, data = d_cl) 
did_unres_mat_f_only <- feols(mat_std ~ migr_fa_only + w1mat_std | schids, data = d_cl) 
did_unres_mat_f <- feols(mat_std ~ migr_fa + w1mat_std | schids, data = d_cl) 
did_unres_mat_both <- feols(mat_std ~ migr_both + w1mat_std | schids, data = d_cl)
```

Results
```{r}
models_unres_mat <- list(
did_unres_mat,
did_unres_mat_m_only,
did_unres_mat_m,
did_unres_mat_f,
did_unres_mat_f_only,
did_unres_mat_both) 
models_unres_mat %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
```

Regressing on English score
```{r}
did_unres_eng <- feols(eng_std ~ migr + w1eng_std | schids, data = d_cl) 
did_unres_eng_m <- feols(eng_std ~ migr_mo + w1eng_std | schids, data = d_cl)
did_unres_eng_m_only <- feols(eng_std ~ migr_mo_only + w1eng_std | schids, data = d_cl) 
did_unres_eng_f <- feols(eng_std ~ migr_fa + w1eng_std | schids, data = d_cl) 
did_unres_eng_f_only <- feols(eng_std ~ migr_fa_only + w1eng_std | schids, data = d_cl) 
did_unres_eng_both <- feols(eng_std ~ migr_both + w1eng_std | schids, data = d_cl)
```

Results
```{r}
models_unres_eng <- list(
did_unres_eng,
did_unres_eng_m_only,
did_unres_eng_m,
did_unres_eng_f,
did_unres_eng_f_only,
did_unres_eng_both) 
models_unres_eng %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
```

## DID adjusted
$$\Delta score_{i,s} = \alpha + \beta \cdot migr_{i,s} + \gamma \cdot FE_{s} + \theta \cdot X_{i,s} + \varepsilon_{i,s}$$
$$X_{i,s}$$ denotes a vector of covariates about the characteristics of students, parents, and households.
